The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-04 paper.tex
update

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

We integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (starlight) in order to\
facilitate a reliable interpretation of simulated gamma-ray map.

>>>>

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

We integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight) in order to\
facilitate a reliable interpretation of simulated gamma-ray spectrum.
